Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe

### 2023-07-18 NSM_Skinner_Wise/NSM_mixing.tex
Added separate directory for arXiv submission. Added Data Availability section and adjusted abstract to fit the word limit.

% Abstract of the paper
\begin{abstract}
The exact evolution of elements in the universe, from primordial hydrogen and helium to heavier elements like gold and platinum produced via the r-process, is still under scrutiny. The supernova deaths of the very first stars to form in the universe led to the enrichment of their local environments with new metals, and can leave behind neutron stars as remnants. These compact objects can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to take place. In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution in order to understand the impact on the second generation of stars and their metal abundances. We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time. We find that in general, a NSM leads to a significant r-process enhancement in the second generation of stars. A high explosion energy leads to almost all enhanced r-process stars being highly r-process enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly r-process enhanced. When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly r-process enhanced compared to longer delay times. This work represents a stepping stone towards understanding how these events impact their environments and metal abundances of descendant generations of stars.
\end{abstract}

@@

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

>>>>

% Abstract of the paper
\begin{abstract}
	The exact evolution of elements in the universe, from primordial hydrogen and helium to heavier elements like gold and platinum produced via the r-process, is still under scrutiny. The supernova deaths of the very first stars to form in the universe led to the enrichment of their local environments with new metals, and can leave behind neutron stars as remnants. These remnants can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to occur. In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution to understand the impact on the second generation of stars and their metal abundances. We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time. In general, a NSM leads to a significant r-process enhancement in the second generation of stars. A high explosion energy leads to almost all enhanced r-process stars being highly enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly enhanced. When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly enhanced compared to longer delay times. This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
\end{abstract}

@@

The data presented in this work is available upon reasonable request to the corresponding author.
